How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-15 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

\noindent
Thank you for bring up this point. To explain our intent, boundary-integral equations can be considered `highly accurate' because of their spectral accuracy (i.e. exponential rate of convergence), and they can be considered `highly efficient' due to the reduction of dimension, i.e. only a boundary needs to be resolved rather than the interior of the domain. This later point regarding the efficiency of a BIE is briefly explained in the first paragraph of Section 3.1.
We agree, though, that in the original manuscript such meanings were not adequately conveyed by the terms `highly accurate' and `highly efficient'. We have therefore either removed these terms or  replaced them with more precise descriptors in all instances. For example, in the second paragraph of the introduction, we have modified the first sentence to read: ``Our method merges spectrally-accurate boundary-integral equation (BIE) methods...''

@@

\noindent
This is a good question, and one that is much more complex than it appears. In short, the range of Reynolds numbers found in natural porous media is too vast to summarize by a typical value. For illustration, Fig.~5.3.1 in Bear's textbook (among the most widely used references for porous media) shows a Reynolds number range of $10^{-2}$ to $10^{3}$ for porous-media {\em laboratory experiments}. The range found in natural materials, which even Bear does not give, would be expected to be even greater. The reason being that the Reynolds number depends on not only the mean particle diameter (for which there are neat tables) but also the typical specific discharge, which can be arbitrarily slow or arbitrarily fast (for example, a flood moving through loose gravel) in natural settings.
Considerable attention has been given to the question of when the low-Reynolds approximation is valid for porous-media applications (see for example, section 5.3 of Bear).
It is fair to say that the Stokes regime reasonably applies to {\em many} groundwater situations, but it would be difficult to justify a stronger statement. Such a complex discussion would be appropriate for a groundwater-engineering article, but lies outside of the scope of our article. We have therefore removed any discussion about typical flow regimes of natural porous media, as we believe such a discussion would distract from the main points of our paper.
\\ \\

@@

This is a good question and, admittedly, a point that was glossed over in the original manuscript. The reason that total anisotropy can be regarded as the produce of shape and configurational anisotropy essential boils down to a dimensional analysis argument.

>>>>

\noindent
Thank you for bringing up this point. To explain our intent, boundary-integral equations can be considered `highly accurate' because of their spectral accuracy (i.e. exponential rate of convergence), and they can be considered `highly efficient' due to the reduction of dimension, i.e. only a boundary needs to be resolved rather than the interior of the domain. This later point regarding the efficiency of a BIE is briefly explained in the first paragraph of Section 3.1.
We agree, though, that in the original manuscript such meanings were not adequately conveyed by the terms `highly accurate' and `highly efficient'. We have therefore either removed these terms or  replaced them with more precise descriptors in all instances. For example, in the second paragraph of the introduction, we have modified the first sentence to read: ``Our method merges spectrally-accurate boundary-integral equation (BIE) methods...''

@@

\noindent
This is a good question, and one that is more complex than it appears. In short, the range of Reynolds numbers found in natural porous media is too vast to summarize by a typical value. For illustration, Fig.~5.3.1 in Bear's textbook (among the most widely used references for porous media) shows a Reynolds number range of $10^{-2}$ to $10^{3}$ for porous-media {\em laboratory experiments}. The range found in natural materials, which even Bear does not give, would be expected to be even greater. The reason being that the Reynolds number depends on not only the mean particle diameter (for which there are neat tables) but also the typical specific discharge, which can be arbitrarily slow or arbitrarily fast (for example, a flood moving through loose gravel) in natural settings.
Considerable attention has been given to the question of when the low-Reynolds approximation is valid for porous-media applications (see for example, section 5.3 of Bear).
It is fair to say that the Stokes regime reasonably applies to {\em many} groundwater situations, but it would be difficult to justify a stronger statement. Such a complex discussion would be appropriate for a groundwater-engineering article, but lies outside of the scope of our article. We have therefore removed any discussion about typical flow regimes of natural porous media, as we believe such a discussion would distract from the main points of our paper.
\\ \\

@@

This is a good question and, admittedly, a point that was glossed over in the original manuscript. The reason that total anisotropy can be regarded as the product of shape and configurational anisotropy essential boils down to a dimensional analysis argument.
